\documentclass[a4paper]{article}

\usepackage[utf8]{inputenc}   % Enter your text in ISO-Latin 1
\usepackage{graphicx}
\bibliographystyle{plain}
\usepackage[citestyle=numeric]{biblatex}
\usepackage{textcomp}

\newcommand{\Q}[2]{
  \textbf{#1} \textit{#2}
 }
\newcommand{\A}[1]{ #1 \\ }

\title{Home Assignment 2 \\ EITN41}
\author{Anon}
\date{}

\begin{document}
\maketitle

\Q{A-6} {
  What is the purpose of the random values $R_1$ in a Mix?
}

\A{
  blah
}

\Q{A-7} {
  When sending a mail through several Mixes, there are several public keys 
  involved: $K_1,K_2, . . . ,K_n$ and $K_a$. 
  What happens if one does not use $K_a$? 
  Does this risk the anonymity of the sender?
}

\A{
  blah
}

\Q{A-8} {
 Briefly explain how using several Mixes versus an onion routing 
 circuit differ both in terms of latency and in cryptographic 
 primitives used for encrypting the traffic. 
}

\A{
  blah
}

\Q{A-12} {
  Regarding replay attacks on Mixes, two protections are suggested in the lecture notes. 
  Which? Would you say that any of them is the better choice?
  Show how the two strategies can be combined and how this
  can make the protection more efficient.
}

\A{
  blah
}

\Q{A-13} {
  It is straightforward to generalize the N - 1 attack to an 
  N - k attack, 0 $<$ k $<$ N. Describe the N - k attack.
}

\A{
  blah
}

\Q{A-15} {
  In the disclosure attack on mixes, 
  explain m, N, n and why a Mix is insecure if $m \leq [N / n]$.
}

\A{
  blah
}

\Q{A-26} {
  A TCP handshake consists of the client and the server exchanging 
  three messages: SYN, SYN-ACK and ACK. 
  Explain why, in Tor, Alice can connect to a webserver and expect 
  the TCP handshake with the
  server to be performed with low latency.
}

\A{
  blah
}

\Q{A-28} {
  Show that the SSL/TLS handshake, when RSA is used, 
  does not provide perfect forward secrecy.
}

\A{
  blah
}

% \begin{thebibliography}{9}
  % \bibitem{cossim} \url{https://en.wikipedia.org/wiki/Cosine_similarity}
% \end{thebibliography}

% Uploaded file: A.pdf
% File saved as: a4c2b8ad79eabee2_HA1_solution.pdf

\end{document}